Cannibalism among the supermassive black holes

### 2019-02-19 paper.tex
Added/change more BH plots.  Re-organized results sections.

@@

Finally, the black hole xray luminosity is estimated from [NEED TO ADD INAYOSHI INEFFICIENCY--PLOTS AND BACKGROUND]:
\begin{equation}
    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}.
\end{equation}

@@

\subsection{Description of Simulations}
\begin{table*}
\centering
\caption{Galaxy characteristics}
\begin{tabular}{c| c c| c c| c c}
 & \multicolumn{2}{c}{$M_{gal}$ [$M_{\odot}$]} & 
\multicolumn{2}{c}{$M_{*}$ [$M_{\odot}$]} & 
\multicolumn{2}{c}{$M_{BH}$ [$M_{\odot}$]} \\
\hline
Galaxy & Init & Final & Init & Final & Init & Final \\
 \hline
A & $7.42\times10^{11}$ & $1.09\times10^{14}$  & $1.22\times10^{11}$ & $1.75\times10^{13}$ & $4.80\times10^{6}$ & $2.19\times10^{9}$\\
B & $1.11\times10^{12}$ & $3.41\times10^{13}$ & $1.80\mathrm{3}{11}$ & $5.58\times10^{12}$ & $1.94\times10^{8}$ & $1.46\times10^{9}$\\
C & $7.23\times10^{10}$ & $3.48\times10^{12}$ & $1.18\times10^{10}$ & $5.68\times10^{11}$ & $9.47\times10^{4}$ & $2.70\times10^{8}$\\
D & $3.92\times10^{10}$ & $1.34\times10^{12}$ & $6.47\times10^{9}$ & $2.20\times10^{11}$ & $9.95\times10^{5}$ & $8.32\times10^{7}$\\
\end{tabular}
\end{table*}

\section{Results}\label{sec:results}
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{"plots/Fractions All Galaxies".png}
\caption{Fractions Merged/Ejected/Orbiting at z=0, by mass bin}
\label{fig:fmeo}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Oriting BHs".png}
\caption{Luminosities of Orbiting BHs at z=0}
\label{fig:loobhs}
\end{center}
\end{figure}

\section{Conclusions}\label{sec:conclusions}
What do we want to say?

\section*{Acknowledgements}

The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data. AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.

>>>>

\section{Results}\label{sec:results}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{"plots/Fractions All Galaxies".png}
\caption{Fractions Merged/Ejected/Orbiting at z=0, by mass bin}
\label{fig:fmeo}
\end{center}
\end{figure}

@@

Finally, the black hole xray luminosity is estimated from:
\begin{equation}
    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}.
\end{equation}

@@

\begin{figure}[htp]
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/radiative_efficiency.png}
\caption{Radiative efficiency of Orbiting Black Holes at z=0}
\label{fig:rad_eff}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Orbiting BHs".png}
\caption{Luminosities of Orbiting BHs at z=0}
\label{fig:loobhs}
\end{center}
\end{figure}

\section{Conclusions}\label{sec:conclusions}

\section{Acknowledgements}
The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data. AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.
